---
title: "P8123_final_project"
author: "Chenxi Liu"
date: "12/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(haven)
library(tidyverse)
library(survey)
```


```{r}
bmi_data = read_xpt(
  "./data/BMX_G.XPT"
  ) %>% select (SEQN, BMXBMI, BMDBMIC) %>%
  rename(BMI = BMXBMI) %>%
  mutate(child_BMI = 
           case_when(BMDBMIC == 1 ~"Underweight",
            BMDBMIC == 2 ~ "Normal",
            BMDBMIC == 3 ~ "Overweight",
            BMDBMIC == 4 ~ "Obese")) %>%
  select(SEQN, BMI, child_BMI) %>%
  drop_na(BMI)

demo = read_xpt(
  "./data/DEMO_G.XPT"
  ) %>%
  select(SEQN, RIAGENDR, RIDAGEYR, RIDRETH1, INDFMPIR, SDMVPSU, SDMVSTRA) %>%
  rename(PIR = INDFMPIR,
         PSU = SDMVPSU,
         strata = SDMVSTRA,
         age = RIDAGEYR) %>%
  mutate(sex = case_when(RIAGENDR == 1 ~"Male",
                         RIAGENDR == 2 ~ "Female"),
         age_group = case_when(age >= 6 & age < 12 ~ "6 – 12",
                         age >= 12 & age < 20 ~ "12 to <20",
                         age >= 20 & age < 40 ~ "20 to <40",
                         age >= 40 & age < 60 ~ "40 to <60",
                         age >=60 & age <= 80 ~"60 - 80"),
        race = case_when(RIDRETH1 == 1 ~ "Mexican American",
                         RIDRETH1 == 2 ~"Other Hispanic",
                         RIDRETH1 ==3 ~"Non-Hispanic White",
                         RIDRETH1 == 4 ~ "Non-Hispanic Black",
                         RIDRETH1 == 5 ~ "Other race/multiracial" )) %>%
  select(SEQN, PSU, strata, sex, age_group, age, race, PIR)

t_data = read_xpt(
  "./data/TST_G.XPT"
  ) %>%
  drop_na() %>%
  rename(T = LBXTST)

# final merged dataset
survey_df = read_xpt(
  "./data/PHTHTE_G.XPT"
  ) %>%
  drop_na() %>%
  inner_join(t_data, by = "SEQN") %>%
  left_join(demo, by = "SEQN") %>%
  left_join(bmi_data, by = "SEQN") %>%
  rename(MEHP = URXMHP,
         MEHHP = URXMHH,
         MEOHP = URXMOH,
         MECPP = URXECP,
         MBzP = URXMZP,
         MBP = URXMBP,
         MiBP = URXMIB,
         MEP = URXMEP,
         MCPP = URXMC1,
         MCNP = URXCNP,
         MCOP = URXCOP,
         MiNP = URXMNP,
         MnMP = URXMNM)
```

## Table 1. Population Characteristics in NHANES Participants With Phthalate and T Data 2011–2012 (n = 2208)

\begin{tabular}{lll}
\hline & & Weighted Median \\
& n & (25th, 75th (Weighted \%) Percentile) \\
\hline Age group, y & & $41(23,56)$ \\
$6-12$ & $293(6.63)$ & \\
12 to $<20$ & $351(12.0)$ & \\
20 to $<40$ & $572(29.5)$ & \\
40 to $<60$ & $507(31.6)$ & \\
$60-80$ & $485(20.2)$ & \\
Sex & & \\
Female & $1098(51.3)$ & \\
Male & $1110(48.7)$ & \\
Race/ethnicity & & \\
Mexican American & $277(8.82)$ & \\
Other Hispanic & $232(7.14)$ & \\
Non-Hispanic white & $742(64.6)$ & \\
Non-Hispanic black & $573(12.2)$ & \\
Other race/multiracial & $384(7.20)$ & \\
PIR continuous & & $2.72(1.26,4.76)$ \\
(no units) & & \\
BMI continuous, kg/m $^{2}$ & & $26.5(22.8,31)$ \\
Child/adolescent BMI & & \\
$\quad$ categories $^{2}$ & & \\
Underweight & $18(2.86)$ & \\
Normal weight & $370(57.8)$ & \\
Overweight & $109(17.7)$ & \\
Obese & $141(21.6)$ & \\
\hline
\end{tabular}

```{r}
table_1 = survey_df %>%
  select(SEQN,  sex, age_group, age, race, PIR, BMI, child_BMI)
table_1 %>% count(age_group) 
table_1 %>% count(sex)
table_1 %>% count(race) 
table_1 %>% drop_na(child_BMI) %>% count(child_BMI) 
```

```{r}
prop.table(svytable(~sex, dclus1))
```

```{r}
prop.table(svytable(~age_group, dclus1))
```

```{r}
prop.table(svytable(~race, dclus1))
```

```{r}
prop.table(svytable(~child_BMI, dclus1))
```


```{r}
dclus1 = svydesign(id = ~SEQN, weights = ~WTSA2YR, strata =  ~strata, data = survey_df)

svyquantile(~age, dclus1, c(.25, .5, .75))

svyquantile(~PIR, dclus1, c(.25, .5, .75))

svyquantile(~BMI, dclus1, c(.25, .5, .75))
```

## Table 2 Creatinine Corrected Urinary Phthalate Metabolite (ng/mL) and Serum T (ng/dL) Medians (25th, 75th percentiles) by Age and Sex Categories in Weighted NHANES Data 2011–2012

```{r}
table2 = survey_df %>%
  mutate(across(MCNP:URXMHNC, ~.x/(URXUCR*0.01))) %>%
  select(SEQN, sex, age_group, everything())

tab2 <- table2 %>%
  group_by(sex, age_group)

table2_groups = group_split(tab2)

# Female 12 -20
head(table2_groups[[1]])
dclus2 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[1]])
svyquantile(~MEHP, dclus2, c(.25, .5, .75))
svyquantile(~MEHHP, dclus2, c(.25, .5, .75))
svyquantile(~MEOHP, dclus2, c(.25, .5, .75))
svyquantile(~MECPP, dclus2, c(.25, .5, .75))
svyquantile(~MBzP, dclus2, c(.25, .5, .75))
svyquantile(~MBP, dclus2, c(.25, .5, .75))
svyquantile(~MiBP, dclus2, c(.25, .5, .75))
svyquantile(~MEP, dclus2, c(.25, .5, .75))
svyquantile(~MCPP, dclus2, c(.25, .5, .75))
svyquantile(~MCNP, dclus2, c(.25, .5, .75))
svyquantile(~MCOP, dclus2, c(.25, .5, .75))
svyquantile(~MiNP, dclus2, c(.25, .5, .75))
svyquantile(~MnMP, dclus2, c(.25, .5, .75))
svyquantile(~T, dclus2, c(.25, .5, .75))

# Female 20 - 40
head(table2_groups[[2]])
dclus3 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[2]])
svyquantile(~MEHP, dclus3, c(.25, .5, .75))
svyquantile(~MEHHP, dclus3, c(.25, .5, .75))
svyquantile(~MEOHP, dclus3, c(.25, .5, .75))
svyquantile(~MECPP, dclus3, c(.25, .5, .75))
svyquantile(~MBzP, dclus3, c(.25, .5, .75))
svyquantile(~MBP, dclus3, c(.25, .5, .75))
svyquantile(~MiBP, dclus3, c(.25, .5, .75))
svyquantile(~MEP, dclus3, c(.25, .5, .75))
svyquantile(~MCPP, dclus3, c(.25, .5, .75))
svyquantile(~MCNP, dclus3, c(.25, .5, .75))
svyquantile(~MCOP, dclus3, c(.25, .5, .75))
svyquantile(~MiNP, dclus3, c(.25, .5, .75))
svyquantile(~MnMP, dclus3, c(.25, .5, .75))
svyquantile(~T, dclus3, c(.25, .5, .75))

# Female 40 - 60
head(table2_groups[[3]])
dclus4 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[3]])
svyquantile(~MEHP, dclus4, c(.25, .5, .75))
svyquantile(~MEHHP, dclus4, c(.25, .5, .75))
svyquantile(~MEOHP, dclus4, c(.25, .5, .75))
svyquantile(~MECPP, dclus4, c(.25, .5, .75))
svyquantile(~MBzP, dclus4, c(.25, .5, .75))
svyquantile(~MBP, dclus4, c(.25, .5, .75))
svyquantile(~MiBP, dclus4, c(.25, .5, .75))
svyquantile(~MEP, dclus4, c(.25, .5, .75))
svyquantile(~MCPP, dclus4, c(.25, .5, .75))
svyquantile(~MCNP, dclus4, c(.25, .5, .75))
svyquantile(~MCOP, dclus4, c(.25, .5, .75))
svyquantile(~MiNP, dclus4, c(.25, .5, .75))
svyquantile(~MnMP, dclus4, c(.25, .5, .75))
svyquantile(~T, dclus4, c(.25, .5, .75))

# Female 6 - 12
head(table2_groups[[4]])
dclus5 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[4]])
svyquantile(~MEHP, dclus5, c(.25, .5, .75))
svyquantile(~MEHHP, dclus5, c(.25, .5, .75))
svyquantile(~MEOHP, dclus5, c(.25, .5, .75))
svyquantile(~MECPP, dclus5, c(.25, .5, .75))
svyquantile(~MBzP, dclus5, c(.25, .5, .75))
svyquantile(~MBP, dclus5, c(.25, .5, .75))
svyquantile(~MiBP, dclus5, c(.25, .5, .75))
svyquantile(~MEP, dclus5, c(.25, .5, .75))
svyquantile(~MCPP, dclus5, c(.25, .5, .75))
svyquantile(~MCNP, dclus5, c(.25, .5, .75))
svyquantile(~MCOP, dclus5, c(.25, .5, .75))
svyquantile(~MiNP, dclus5, c(.25, .5, .75))
svyquantile(~MnMP, dclus5, c(.25, .5, .75))
svyquantile(~T, dclus5, c(.25, .5, .75))

# Female 60 -80
head(table2_groups[[5]])
dclus6 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[5]])
svyquantile(~MEHP, dclus6, c(.25, .5, .75))
svyquantile(~MEHHP, dclus6, c(.25, .5, .75))
svyquantile(~MEOHP, dclus6, c(.25, .5, .75))
svyquantile(~MECPP, dclus6, c(.25, .5, .75))
svyquantile(~MBzP, dclus6, c(.25, .5, .75))
svyquantile(~MBP, dclus6, c(.25, .5, .75))
svyquantile(~MiBP, dclus6, c(.25, .5, .75))
svyquantile(~MEP, dclus6, c(.25, .5, .75))
svyquantile(~MCPP, dclus6, c(.25, .5, .75))
svyquantile(~MCNP, dclus6, c(.25, .5, .75))
svyquantile(~MCOP, dclus6, c(.25, .5, .75))
svyquantile(~MiNP, dclus6, c(.25, .5, .75))
svyquantile(~MnMP, dclus6, c(.25, .5, .75))
svyquantile(~T, dclus6, c(.25, .5, .75))

# Male 12 - 20
head(table2_groups[[6]])
dclus7 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[6]])
svyquantile(~MEHP, dclus7, c(.25, .5, .75))
svyquantile(~MEHHP, dclus7, c(.25, .5, .75))
svyquantile(~MEOHP, dclus7, c(.25, .5, .75))
svyquantile(~MECPP, dclus7, c(.25, .5, .75))
svyquantile(~MBzP, dclus7, c(.25, .5, .75))
svyquantile(~MBP, dclus7, c(.25, .5, .75))
svyquantile(~MiBP, dclus7, c(.25, .5, .75))
svyquantile(~MEP, dclus7, c(.25, .5, .75))
svyquantile(~MCPP, dclus7, c(.25, .5, .75))
svyquantile(~MCNP, dclus7, c(.25, .5, .75))
svyquantile(~MCOP, dclus7, c(.25, .5, .75))
svyquantile(~MiNP, dclus7, c(.25, .5, .75))
svyquantile(~MnMP, dclus7, c(.25, .5, .75))
svyquantile(~T, dclus7, c(.25, .5, .75))

# Male 20 -40
head(table2_groups[[7]])
dclus8 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[7]])
svyquantile(~MEHP, dclus8, c(.25, .5, .75))
svyquantile(~MEHHP, dclus8, c(.25, .5, .75))
svyquantile(~MEOHP, dclus8, c(.25, .5, .75))
svyquantile(~MECPP, dclus8, c(.25, .5, .75))
svyquantile(~MBzP, dclus8, c(.25, .5, .75))
svyquantile(~MBP, dclus8, c(.25, .5, .75))
svyquantile(~MiBP, dclus8, c(.25, .5, .75))
svyquantile(~MEP, dclus8, c(.25, .5, .75))
svyquantile(~MCPP, dclus8, c(.25, .5, .75))
svyquantile(~MCNP, dclus8, c(.25, .5, .75))
svyquantile(~MCOP, dclus8, c(.25, .5, .75))
svyquantile(~MiNP, dclus8, c(.25, .5, .75))
svyquantile(~MnMP, dclus8, c(.25, .5, .75))
svyquantile(~T, dclus8, c(.25, .5, .75))

# Male 40 -60
head(table2_groups[[8]])
dclus9 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[8]])
svyquantile(~MEHP, dclus9, c(.25, .5, .75))
svyquantile(~MEHHP, dclus9, c(.25, .5, .75))
svyquantile(~MEOHP, dclus9, c(.25, .5, .75))
svyquantile(~MECPP, dclus9, c(.25, .5, .75))
svyquantile(~MBzP, dclus9, c(.25, .5, .75))
svyquantile(~MBP, dclus9, c(.25, .5, .75))
svyquantile(~MiBP, dclus9, c(.25, .5, .75))
svyquantile(~MEP, dclus9, c(.25, .5, .75))
svyquantile(~MCPP, dclus9, c(.25, .5, .75))
svyquantile(~MCNP, dclus9, c(.25, .5, .75))
svyquantile(~MCOP, dclus9, c(.25, .5, .75))
svyquantile(~MiNP, dclus9, c(.25, .5, .75))
svyquantile(~MnMP, dclus9, c(.25, .5, .75))
svyquantile(~T, dclus9, c(.25, .5, .75))

# Male 6-12
head(table2_groups[[9]])
dclus10 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[9]])
svyquantile(~MEHP, dclus10, c(.25, .5, .75))
svyquantile(~MEHHP, dclus10, c(.25, .5, .75))
svyquantile(~MEOHP, dclus10, c(.25, .5, .75))
svyquantile(~MECPP, dclus10, c(.25, .5, .75))
svyquantile(~MBzP, dclus10, c(.25, .5, .75))
svyquantile(~MBP, dclus10, c(.25, .5, .75))
svyquantile(~MiBP, dclus10, c(.25, .5, .75))
svyquantile(~MEP, dclus10, c(.25, .5, .75))
svyquantile(~MCPP, dclus10, c(.25, .5, .75))
svyquantile(~MCNP, dclus10, c(.25, .5, .75))
svyquantile(~MCOP, dclus10, c(.25, .5, .75))
svyquantile(~MiNP, dclus10, c(.25, .5, .75))
svyquantile(~MnMP, dclus10, c(.25, .5, .75))
svyquantile(~T, dclus10, c(.25, .5, .75))

# Male 60 - 80
head(table2_groups[[10]])
dclus11 = svydesign(id = ~SEQN, weights = ~WTSA2YR, data = table2_groups[[10]])
svyquantile(~MEHP, dclus11, c(.25, .5, .75))
svyquantile(~MEHHP, dclus11, c(.25, .5, .75))
svyquantile(~MEOHP, dclus11, c(.25, .5, .75))
svyquantile(~MECPP, dclus11, c(.25, .5, .75))
svyquantile(~MBzP, dclus11, c(.25, .5, .75))
svyquantile(~MBP, dclus11, c(.25, .5, .75))
svyquantile(~MiBP, dclus11, c(.25, .5, .75))
svyquantile(~MEP, dclus11, c(.25, .5, .75))
svyquantile(~MCPP, dclus11, c(.25, .5, .75))
svyquantile(~MCNP, dclus11, c(.25, .5, .75))
svyquantile(~MCOP, dclus11, c(.25, .5, .75))
svyquantile(~MiNP, dclus11, c(.25, .5, .75))
svyquantile(~MnMP, dclus11, c(.25, .5, .75))
svyquantile(~T, dclus11, c(.25, .5, .75))

```

